On Secure Delegation of SampBQP with a Classical Client

### 2020-02-07 bqp.tex
Write protocol for FBQP

In this section we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
\begin{thm}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.

Let $L\in\BQP$, and $x\in\set{0,1}^n$.
We start with an overview of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.
We'll summarize some more relevant details of this construction in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.

\begin{protocol}{Verifying yes-instances for $\BQP$}
	\label{proto:BQP}
	\begin{enumerate}
		\item The verifier chooses some tensor product of $X$ and $Z$ measurements $\Lambda$
		\item The prover sends the verifier some state $\rho\in\cB^{\otimes m}$ qubit-by-qubit.
		\item The verifier measures $\rho$ according to $S$
		\item The verifier decides whether to accept based on the measurement results.
	\end{enumerate}
\end{protocol}

\cref{proto:BQP} has negligible completeness and soundness. \Ethan{Elaborate or no?}

Now we compile \cref{proto:BQP} using $\mathsf{QHE}$ in order to achieve blindness.
We denote the honest prover's action in \cref{proto:BQP} as $\cF$.

@@

Mahadev's protocol compiles QPIP1 to QPIP0 but deteriorates soundness, and \cite{parallelrep} says parallel repetition works to recover good soundness guarantees.
\Ethan{TODO elaborate}

\begin{rmk}
	Our protocol for $\BQP$ can easily be generalized to $\FBQP$ too in the following way:
	\Ethan{TODO actually need 2 copies per bit now}
\end{rmk}

>>>>

In this section we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
\begin{thm}
	\label{thm:QPIP0BQP}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.

Let $L\in\BQP$, and $x\in\set{0,1}^n$.
We start with an overview of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.

\begin{protocol}{Verifying yes-instances for $\BQP$}
	\label{proto:BQP}
	We give only a high-level description here.
	For more details, see \cref{AlgGroundStateCheck} where we generalize this for $\SampBQP$.
	\begin{enumerate}
		\item The verifier chooses some tensor product of $X$ and $Z$ measurements $\Lambda$
		\item The prover sends the verifier some state $\rho\in\cB^{\otimes m}$ qubit-by-qubit.
		\item The verifier measures $\rho$ according to $S$
		\item The verifier decides whether to accept based on the measurement results.
	\end{enumerate}
\end{protocol}

Differently from \cref{AlgGroundStateCheck}, \cref{proto:BQP} has negligible completeness and soundness, due to parallel repetition.
We denote the honest prover's action in \cref{proto:BQP} as $\cF$.
Now we compile it using $\mathsf{QHE}$ in order to also achieve blindness:

@@

\cite{mahadev_delegation} gives a compiler from $\QPIP_1$ protocols of the form in \cref{proto:BQP} to $\QPIP_0$ but deteriorates soundness.
Note that \cref{proto:BlindBQP} can also be collapsed into the same form, so the same compiler can also be applied to it to obtain a $\QPIP_0$ protocol.

We can then use results from \cite{parallelrep} to apply parallel repetition and recover the negligible soundness.

Our results for $\BQP$ can also be generalized to $\FBQP$ by applying $2n$ copies of \cref{thm:QPIP0BQP} in parallel.

\begin{protocol}{Blind and verifiable $\QPIP_0$ delegation for $\FBQP$}
	\label{QPIP0FBQP}
	Suppose $y\in\set{0,1}^m$ is the output of our $\FBQP$ instance.
	\begin{enumerate}
		\item Apply \cref{thm:QPIP0BQP} to every $y_i=0$ and $y_i=1$ case in parallel, resulting in a total of $2m$ cases.
		\item Output $y$ if for each $i$ precisely one of the $y_i=0$ and $y=i=1$ cases accepts.
	\end{enumerate}
\end{protocol}

\Ethan{TODO prove that \cref{QPIP0FBQP} actually works as expected}
